---
title: "Pocket Money"
---

```{r}
#| label: setup
library(tidyverse)
library(ggformula)
library(crosstable)
library(mosaic)
```

```{r}
pmoney <- read.csv("../../data/PocketMoney.csv")
pmoney
```

This dataset consists of 1 quant and 3 qual variables

### Data Dictionary

-   S.No - Qualitative

-   Name - Qualitative

-   Gender - Qualitative

-   Money_Spent - Quantitative

```{r}
pmoney_modified <-pmoney %>% 
  dplyr::mutate(
    Gender = as_factor(Gender)
  )
pmoney_modified
```

```{r}
pmoney_modified %>%
  gf_density(
    ~ Money_spent,
    fill = ~ Gender,
    alpha = 0.5,
    title = "Money spent",
    subtitle = "Male vs Female"
  )
pmoney_modified %>%
  gf_boxplot(
    Money_spent ~ Gender,
    fill = ~ Gender,
    alpha = 0.5,
    title = "Math Anxiety Score Box Plots",
    subtitle = "Boys vs Girls"
  ) 
##
pmoney_modified %>% count(Gender)
pmoney_modified %>% 
  group_by(Gender) %>% 
  summarise(mean = mean(Money_spent))
```

### Inference

-   Majority of people, men and female included spend around 0 to a few hundreds per day

-   Men seem to spend a little more than women not including outliers

-   There is a pretty big overlap in general in the male and female category

-   The graph is left-skewed with one peak

-   In boxplot, median value is similar in both categories

-   There is more variance in the male category above the median

-   There are few outliers in both categories

-   Mean money spent of male (748.6) is larger than female (693.3)which means on average, males spend more

```{r}
gf_histogram(~Money_spent,fill=~	
Gender,data=pmoney_modified,bins = 100)
```

### Inference

-   most people spend from around 0 to a few hundreds

-   most people spend under 2000 per day expect a few outliers

-   males on average spend slightly more than females

```{r}
pmoney_modified %>%
  gf_density( ~ Money_spent,
              fill = ~ Gender,
              alpha = 0.5,
              title = "Money spent for males and females") %>%
  gf_facet_grid(~ Gender) %>% 
  gf_fitdistr(dist = "dnorm") 
##
pmoney_modified %>% 
  gf_qqline(~ Money_spent, color = ~ Gender,
            title = "Money Spent..is it Normally Distributed?") %>%
  gf_qq() %>% 
  gf_facet_wrap(~ Gender)  # independent y-axis
##
male_moneyspent <- pmoney_modified %>% 
  filter(Gender== "Male") %>% 
  select(Money_spent)
##
female_moneyspent <- pmoney_modified %>% 
  filter(Gender== "Female") %>% 
  select(Money_spent)
```

### Inference

-   both of the graphs are left skewed for both male and female

-   the density curve of both graphs do not align with the normal fit curve which suggests the distribution may not be normal

-   In the qq plot, the dots are close to the normal but do not align perfectly to it, there are also outliers in both categories

```{r}
shapiro.test(male_moneyspent$Money_spent)
shapiro.test(female_moneyspent$Money_spent)
```

### Inference

-   Since the p-value is less than 0.05 in both categories, it indicates that the data significantly deviates from a normal distribution. This means that the money spent by males and that spent by females are both not normally distributed

## Variance Test

var.test() is designed to perform an F-test to compare the variances of two groups

```{r}
var.test(Money_spent ~ Gender, data = pmoney_modified, 
         conf.int = TRUE, conf.level = 0.95) %>% 
  broom::tidy()

```

### Inference

-   since the p-value is higher than 0.05, there is not significant difference in variance between the two groups

```{r}
qf(0.646,40,40)

```

This output indicates that about 64.6% of the area under the F-distribution curve with the specified degrees of freedom lies to the left of this value.

```{r}
mosaic::t_test(Money_spent ~ Gender, data = pmoney_modified) %>% 
  broom::tidy()
```

### Inference

-   Since p value is greater than 0.05, it indicates that there is no significant difference between the groups, which indicates similar money spending behaviour in male and female categories.

-   Thus null hypothesis cannot be rejected

```{r}
wilcox.test(Money_spent ~ Gender, data = pmoney_modified, 
            conf.int = TRUE, 
            conf.level = 0.95) %>% 
  broom::tidy()
```

-   since p-value is greater than 0.05, there is insufficient evidence to suggest a difference in median money spent between male and female groups

-   the confidence interval shows the range of possible median differences. Since the confidence interval contains 0 within its bounds, this means there is no significant difference between the groups

## Permutation Test

```{r}
null_dist_moneyspent <- 
  do(4999) * diffmean(data = pmoney_modified, Money_spent ~ shuffle(Gender))
null_dist_moneyspent
```

```{r}
obs_diff_moneyspent <- diffmean(Money_spent ~ Gender, data = pmoney_modified) 
obs_diff_moneyspent
```

-   Difference between the mean of money spent in females and males is 55.29

```{r}
gf_histogram(data = null_dist_moneyspent, ~ diffmean, bins = 25) %>%
  gf_vline(xintercept = obs_diff_moneyspent, 
           colour = "red", linewidth = 1,
           title = "Null Distribution by Permutation", 
           subtitle = "Histogram") %>% 
  gf_labs(x = "Difference in Means")
###
gf_ecdf(data = null_dist_moneyspent, ~ diffmean, 
        linewidth = 1) %>%
  gf_vline(xintercept = obs_diff_moneyspent, 
           colour = "red", linewidth = 1,
           title = "Null Distribution by Permutation", 
           subtitle = "Cumulative Density") %>% 
  gf_labs(x = "Difference in Means")
```

### Inference

-   The red line in the graph represents the observed difference in means of the two categories (i.e, -55.29)

-   the histogram represents the null distribution from the permutation tests

-   Since the red line falls within the central range of the null distribution, we can assume that the difference was due to random chance

-   This tells us that the difference between money spent by male and female is not statistically significant

```{r}
1-prop1(~ diffmean <= obs_diff_moneyspent, data = null_dist_moneyspent)
```

-   There is a 56.4% chance that a difference in means equal to or greater than obs_diff_moneyspent could occur under the null hypothesis.

-   since the p-value is higher than 0.05, the observed difference is statistically insignificant, and we cannot reject the null hypothesis

## Conclusion

From our data we can say males on average spend more than women though it is not a significant amount

There is no significant difference between the spending habits of males and females
