---
title: "Class3: Counts and Stuff"
---

## Setup

```{r}
#| label: setup
library(knitr)
library(tidyverse)
library(babynames)
library(ggformula)
library(skimr)
library(kableExtra)
library(mosaic)
```

## Examining Taxi Dataset

```{r}
taxi <- read.csv("https://vincentarelbundock.github.io/Rdatasets/csv/modeldata/taxi.csv")
```

```{r}
taxi
```

```{r}
glimpse(taxi)
```

```{r}
inspect(taxi)
```

```{r}
skim(taxi)
```

```{r}
taxi_modified <- taxi %>%
  mutate(
    dow = factor(dow,
      levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
      labels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
      ordered = TRUE
    ),
    ##
    local = factor(local,
      levels = c("no", "yes"),
      labels = c("no", "yes"),
      ordered = TRUE
    ),
    ##
    month = factor(month,
      levels = c("Jan", "Feb", "Mar", "Apr"),
      labels = c("Jan", "Feb", "Mar", "Apr"),
      ordered = TRUE
    )
  )
taxi_modified %>% glimpse()
```

## Plotting Barcharts for Taxi Dataset

```{r}
gf_bar(~tip, fill = ~local, data = taxi_modified, position = "dodge") %>%
  gf_labs(title = "Plot 1A: Counts of Tips")
```

```{r}
gf_bar(~tip, fill = ~local, data = taxi_modified, position = "stack") %>%
  gf_labs(title = "Plot 1A: Counts of Tips")
```

```{r}
gf_bar(~tip, fill = ~local, data = taxi_modified, position = "fill") %>%
  gf_labs(title = "Plot 1A: Counts of Tips")
```

```{r}
taxi_modified %>%
  gf_bar(~company,
    fill = ~tip,
    position = "dodge"
  ) %>%
  gf_labs(title = "Plot 2A: Dodged Bar Chart") %>%
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))


```

```{r}
taxi_modified %>%
  gf_bar(~company,
    fill = ~tip,
    position = "stack"
  ) %>%
  gf_labs(title = "Plot 2A: Dodged Bar Chart") %>%
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

```{r}
taxi_modified %>%
  gf_bar(~company,
    fill = ~tip,
    position = "fill"
  ) %>%
  gf_labs(title = "Plot 2A: Dodged Bar Chart") %>%
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

```{r}
gf_bar(~hour, fill = ~tip, data = taxi_modified, position ="fill") %>%
  gf_labs(title = "Plot B: Counts of Tips by Hour")
```

```{r}
gf_bar(~dow, fill = ~tip, data = taxi_modified, position = "fill") %>%
  gf_labs(title = "Plot C: Counts of Tips by Day of Week")
```

```{r}
gf_bar(~month, fill = ~tip, data = taxi_modified, position="fill") %>%
  gf_labs(title = "Plot D: Counts of Tips by Month")
```

```{r}
gf_bar(~ month | dow, fill = ~tip, data = taxi_modified, position="fill") %>%
  gf_labs(title = "Plot E: Counts of Tips by Day of Week and Month")
```

```{r}
gf_bar(~ dow | hour, fill = ~tip, data = taxi_modified, position = "fill") %>%
  gf_labs(
    title = "Plot F: Counts of Tips by Hour and Day of Week",
    subtitle = "Is this plot arrangement easy to grasp?"
  )
```

```{r}
gf_bar(~ hour | dow, fill = ~tip, data = taxi_modified, position = "fill") %>%
  gf_labs(
    title = "Plot G: Counts of Tips by Hour and Day of Week",
    subtitle = "Swapped the Facets"
  )
```

```{r}
data(HELPrct)
HELPrct
```

```{r}
gf_bar(~substance,data = mosaicData::HELPrct) %>% 
  gf_labs(title = "Plotting Proportions using gf_props")
```

```{r}
gf_bar(~substance, fill= ~sex, data=HELPrct)

```

# Your Turn Section

## Examining Birthdays Dataset

```{r}
titanic <-read_csv(file = "../../data/titanic.csv")
titanic
```

```{r}
glimpse(titanic)
```

```{r}
skim(titanic)
```

```{r}
inspect(titanic)
```

```{r}
titanic_modified <- titanic %>%
  mutate(
    survived = factor(`survived`,
      levels = c("0", "1"),
      labels = c("no","yes"),
      ordered = TRUE
    ),
    ##
    pclass = factor(`pclass`,
      levels = c("1","2","3"),
      labels = c("1","2","3"),
      ordered = TRUE
    ),
    ##
    sex = factor(sex,
      levels = c("female","male"),
      labels = c("female","male"),
      ordered = TRUE
    )
  )
titanic_modified %>% glimpse()
```

```{r}
gf_bar(~pclass, data = titanic_modified) %>%
  gf_labs(title = "Members of Each Class") %>% 
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

there were there classes of passengers a majority belonging to third class.

```{r}
gf_bar(~survived, data = titanic_modified) %>%
  gf_labs(title = "Count of Surviors") %>% 
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

A majority of the passengers did not survive.

```{r}
gf_bar(~sex, data = titanic_modified,
       fill=~survived) %>%
  gf_labs(title = "Number of Survivors of Men and Women") %>% 
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

```{r}
gf_bar(~sex, data = titanic_modified,
       fill=~survived,
       position="fill") %>%
  gf_labs(title = "Proportion of Survivors of Men and Women") %>% 
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

there were many more female survivors than male

```{r}
gf_bar(~pclass, data = titanic_modified,
       fill=~survived) %>%
  gf_labs(title = "Number of Survivors of Different Classes") %>% 
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

```{r}
gf_bar(~pclass, data = titanic_modified,
       fill=~survived,
       position="fill") %>%
  gf_labs(title = "Proportion of Survivors of Different Classes") %>% 
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

Even though first class has much fewer passengers than third class, it has the highest number of survivors.

```{r}
gf_bar(~parch, data = titanic_modified,
       fill=~survived,
       position="stack") %>%
  gf_labs(title = "Survivors based on number of parents on board") %>% 
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

```{r}
gf_bar(~sibsp, data = titanic_modified,
       fill=~survived,
       position="stack") %>%
  gf_labs(title = "Survivors based on Siblings on board") %>% 
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

```{r}
gf_bar(~pclass|sex, data = titanic_modified,
       fill=~survived,
       position="stack") %>%
  gf_labs(title = "Surviors based on Class and Gender") %>% 
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```
